\section{}
The best way to check which data structure is best for a dictionary is to see which data structure has the best time complexity for the operations.

\subsection*{Linked List}
Linked lists are a time inefficient data structure for a dictionary, because they have a time complexity of $O(n)$ for $insert$ and $rank$, since you have to go through the entire list each time. Additionally, $search$ and $delete$ could be $O(n)$ if the list is not sorted, or $O(\log n)$ if it is sorted. However, they do provide a space efficient data structure, since they only require $O(n)$ space.

\subsection*{Array}
Arrays are a space inefficient data structure, while they do require $O(n)$ space, it is a non-sparse data structure, so it is not as space efficient as a linked list. However, arrays are time efficient for a dictionary, since they have $O(1)$ time complexity for $insert$, $delete$, and $search$. However, $rank$ is $O(n)$, since you have to go through the entire array to find the rank, which is worse than a linked list since the structure could be sparse and have a lot of empty space. 

\subsection*{Hashmap}
A hashmap is a space efficient data structure, since it can be sparse. However, it is not as space efficient as a linked list. $insert$, $delete$, and $search$ are all $O(1)$, which is the best time complexity for a dictionary. However, $rank$ is $O(n)$, since you have to go through the entire hashmap to find the rank, which is worse than a linked list since the structure could be sparse and have a lot of empty space.

\subsection*{Self-Balancing Binary Search Tree}
A self-balancing BST would provide great time complexity for $insert$, $delete$, $search$, and $rank$, since they are all $O(\log n)$. However, it is more space inefficient than a linked list.